---
title: "R replication of thesis"
author: "Andy Shih"
date: "2023-10-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Thesis data analysis - balancing test analysis
# Last modified: 1 Oct, 2023
# Andy Shih

# Load necessary libraries
```{r include=FALSE}
library(openxlsx)
library(dplyr)
```

# Import the data
# Only use data_completed from now on
```{r echo=FALSEm, results='hide'}
setwd("/Users/andy/EUR study/masters thesis work/results/data&analysis/analysis/output")
data_completed <- read.xlsx("/Users/andy/EUR study/masters thesis work/results/data&analysis/analysis/data_completed.xlsx", sheet = "Sheet0", startRow = 1)
```

```{r}
# Drop if gender >= 3
data_completed <- data_completed %>% filter(gender < 3)

# Rename gender to female and change to 0/1
data_completed$female <- data_completed$gender - 1
data_completed <- data_completed %>% select(-gender)

# Rename studying_country to nl and change to 0/1
data_completed$nl <- ifelse(data_completed$studying_country == 1, 1, 0)
data_completed <- data_completed %>% select(-studying_country)

# Create westerner variable
data_completed$westerner <- ifelse(data_completed$raised_region >= 2, 1, 0)

# Rename degree to masters and correct Qualtrics' mistake
data_completed$masters <- ifelse(data_completed$degree == 3, 2, data_completed$degree)
data_completed$masters <- data_completed$masters-1
data_completed <- data_completed %>% select(-degree)

# Create fin_stress variable
data_completed$fin_stress <- ifelse(data_completed$financial <= 2, 1, 0)

# Create edu_mom_b variable
data_completed <- data_completed %>% mutate(edu_mom_b = case_when(.default = 0,
                                                                  edu_mom >= 4 & edu_mom <= 6 ~ 1)) # If there is NA in one var, when I wanna mutate a new var based on this var, if I don't specify explicitly like this, R will still treat the obs with NA as NA in new var. 

# Create edu_dad_b variable
data_completed <- data_completed %>% mutate(edu_dad_b = case_when(.default = 0,
                                                                  edu_dad >= 4 & edu_dad <= 6 ~ 1)) # same as above

# Create lowMentalHealth variable
data_completed$lowMentalHealth <- ifelse(data_completed$subjective_wellbeing %in% c(1, 2), 1, 0)

# PHQ score construction: minus one first and sum them up
phq_vars <- c("phq-1", "phq-2", "phq-3", "phq-4")
data_completed[phq_vars] <- data_completed[phq_vars] - 1
data_completed$phq <- data_completed$phq <- rowSums(data_completed[phq_vars], na.rm = TRUE)

# Recode lang and treatment (the encode equivalation in R is as.numeric(as.factor(the cat var)) or use as.numeric(the cat var) directly, but ifelse in this case is easy)
data_completed$t <- factor(data_completed$treatment)
data_completed$user_lang <- factor(data_completed$lang)
```

# Balancing test for completed data (Table 1)
```{r}
# It's like local to group all the cat and conti var respectively
balancing_cat <- c("female", "nl", "westerner", "masters", "edu_mom_b", "edu_dad_b", "lowMentalHealth", "fin_stress", "user_lang")
balancing_conti <- c("age", "phq")
```

```{r}
for (var in balancing_cat) {
  print(table(data_completed$t, data_completed[[var]]))
  print(t.test(data_completed[[var]] ~ data_completed$t))
}

for (var in balancing_conti) {
  print(summary(data_completed[[var]] ~ data_completed$t, FUN = list(mean = mean, sd = sd)))
  print(t.test(data_completed[[var]] ~ data_completed$t))
}
```


# T test for support receiving for each kind of support
```{r}
for (i in 1:4) {
  data_completed$support <- ifelse(data_completed$supportReceiving == i, 1, 0)
  print(t.test(data_completed$support ~ data_completed$t))
}
```


# T test for support receiving for Any support
```{r}
data_completed$anysupport <- ifelse(data_completed$supportReceiving != 5, 1, 0)
print(t.test(data_completed$anysupport ~ data_completed$t))
```

# The same balance test for TW vs. NL samples (Table A3)
```{r}
balancing_cat_tw_nl <- c("female", "masters", "edu_mom_b", "edu_dad_b", "lowMentalHealth", "fin_stress")
balancing_conti_tw_nl <- c("age", "phq")

for (var in balancing_cat_tw_nl) {
  print(table(data_completed$nl, data_completed[[var]]))
  print(t.test(data_completed[[var]] ~ data_completed$nl))
}

for (var in balancing_conti_tw_nl) {
  print(summaryBy(data_completed[[var]] ~ data_completed$nl, FUN = list(mean = mean, sd = sd)))
  print(t.test(data_completed[[var]] ~ data_completed$nl))
}

# T test for support receiving for each kind of support
for (i in 1:4) {
  data_completed$support <- ifelse(data_completed$supportReceiving == i, 1, 0)
  print(t.test(data_completed$support ~ data_completed$nl))
}

# T test for support receiving for Any support
data_completed$anysupport <- ifelse(data_completed$supportReceiving != 5, 1, 0)
print(t.test(data_completed$anysupport ~ data_completed$nl))

```

# To test attrition (Table A2)
```{r}
# Attrition
attrition_count <- sum(data_completed$emailforcontacting == "" & data_completed$enter_lottery != 2)
cat("Number of people dropped out:", attrition_count, "\n")

# Without control vars
model_without_controls <- lm(finished ~ t, data = data_completed)
summary(model_without_controls)
model_without_controls_r <- coeftest(model_without_controls, vcov. = vcovHC, type = "HC1") # If I assign this coeftest object to a new obj, this panel_PooledOLS_reg_r directly takes the robust SE

stargazer(model_without_controls_r,
          type = "text",
          header = F,
          title = "Attrition test w/o controls")

# Include the Self-reported Mental Health variable instead of PHQ4
# because most respondents who dropped out did not reach PHQ4 questions

# Controls
control_vars <- c("age", "female", "nl", "westerner", "masters", 
                  "edu_mom_b", "edu_dad_b", "lowMentalHealth", "fin_stress")

# With control vars
model_with_controls <- lm(finished ~ t + age + female + nl + westerner + 
                           masters + edu_mom_b + edu_dad_b + lowMentalHealth + fin_stress, 
                         data = data_completed)
summary(model_with_controls)

model_with_controls_r <- coeftest(model_with_controls_r, vcov. = vcovHC, type = "HC1") 

stargazer(model_with_controls_r,
          type = "text",
          header = F,
          title = "Attrition test w/ controls")
```

